### 2023-03-12 main/chapter_2ljets.tex
weaken diboson statement

\subsubsection{Alternative \diboson}
\label{sec:2ljets_diboson_alt}
No complete alternative samples were available for comparison with our central
\diboson\ samples, which are simulated with \sherpa~2.2.2 at NLO with up to six
electroweak vertices.
This limitation is simply a result of how \atlas\ has decided to allocate
its limited resources on, and quite reasonably so, since full simulation is
computationally expensive and \diboson\ processes are relatively rare.
We did, however, have access to the cheaper alternative set of small,
truth-level samples, that were simulated with the same \sherpa\ setup but with
varied parameters to assess uncertainties in the modelling of parton showers.

>>>>

\subsubsection{Alternative \diboson}
\label{sec:2ljets_diboson_alt}
When executing this analysis project, no complete alternative \diboson\ samples
were available in the specific post-processed format required for our analysis'
software framework.
Our central \diboson\ samples are simulated with \sherpa~2.2.2 at NLO with up
to six electroweak vertices, and although \diboson\ sample comparisons are
conditionally recommended by internal
documentation~\cite{atlas_twiki_susytheoretical}, we failed to acquire
alternative samples for this comparison.
This limitation is in part a result of how \atlas\ and our local SUSY group has
decided to allocate its limited resources, and quite reasonably so, since
full simulation and data derivation is expensive in computation and data
storage regards, and \diboson\ processes are relatively rare.
Instead, we followed advice to use the cheaper alternative set of small,
truth-level samples, that were simulated with the same \sherpa\ setup but with
varied parameters to assess uncertainties in the modelling of parton showers.
